---
title: "Group 1 HW 3 - Q2"
author: "Siow Meng Low"
date: "17 December 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Forecasting Model  

In the _Bass Model_ article, the forecasting model is given as below:

\begin{center}
$$F_t = (p + q[C_{t-1} / m])(m - C_{t-1})$$
$$F_t = pm + (q - p) C_{t-1} - \frac{q}{m} C_{t-1}^2$$
\end{center}

The paraemters used in the above equation is described below:  

* $F_t$: Forecasted number of new adopters during time period $t$, denoted as $N(t)$ in the class lecture notes
* $C_{t-1}$: Cumulative number of people who have adopted the product up to time $t - 1$
* $p$: Coefficient of innovation (a.k.a. Rate of spontatneous adoption in the class lecture notes)
* $q$: Coefficient of imitation (a.k.a. Rate of imitation in the class lecture notes)
* $m$: Market size, the number of people estimated to eventually adopt the new product

From the above equation, we can see that $F_t$ is a function of $C_{t-1}$ and $C_{t-1}^2$. In the article, the authors proposed to minimise the sum of squared forecast errors $\sum_{t=1}^{N} E_t^2$ where:  

* $S_t$: the actual number of new adopters in period $t$, denoted as $S(t)$ in the class lecture notes
* $E_t = F_t - S_t$, $E_t$ is the forecast error for period $t$  

This is the same technique used in the Ordinary Least Square Estimation of Linear Regression, where we take $F_t$ (the forecasted number of new adopters in period _t_) to be $\hat{S_t}$ (the estimated number of adopters in period t). The equation for linear regression can be written as:

\begin{center}
$$F_t = \hat{p}\hat{m} + (\hat{q} - \hat{p}) C_{t-1} - \frac{\hat{q}}{\hat{m}} C_{t-1}^2$$
$$\hat{S_t} = \hat{a} + \hat{b} C_{t-1} + \hat{c} C_{t-1}^2$$
\end{center}

where:

\begin{center}
$$\hat{S_t} = F_t$$
$$\hat{a} = \hat{p}\hat{m}$$
$$\hat{b} = \hat{q} - \hat{p}$$
$$\hat{c} = - \frac{\hat{q}}{\hat{m}}$$
\end{center}

The system of equations involving $\hat{p}$, $\hat{q}$, and $\hat{m}$ can be rewritten as follows:

\begin{center}
$$\hat{m} = \frac{-\hat{b} \pm \sqrt{\hat{b}^2 - 4\hat{a}\hat{c}}}{2\hat{c}}$$
$$\hat{p} = \frac{\hat{a}}{\hat{m}}$$
$$\hat{q} = - \hat{c}\hat{m}$$
\end{center}

Note that for $\hat{m}$, we are only interested in its non-negative real root, since the market size should always be greater than or equal to zero.  

In the following section, we shall perform least square regression (dependent variable is $S_t$ and independent variables are $C_{t-1}$ and $C_{t-1}^2$) using R, in order to obtain the rolling horizon estimates of $p$, $q$, $m$, and $F_t$.  

## Rolling Horizon Estimate using Ordinary Least Square Regression  

```{r Libraries, echo = FALSE}
library(pander)
```

The table that contains the box office revenue data of "The Doctor" is included in the CSV file, _TheDoctorData.csv_. First, we shall read the revenue data from the CSV and calculate $C_{t-1}$ for each period.  

```{r ReadData, results = "asis"}
setwd("C:/Users/admin/Desktop/Imperial MSc/Network Analytics/Assignment 3")

doctorData <- read.csv("TheDoctorData.csv")
doctorData$"Ctlag" <- c(0, doctorData$Ct[1:(nrow(doctorData) - 1)])

pander(doctorData, 
       caption = "Revenues and Cumulative Revenues in $ Millions for THE DOCTOR")

```

Next, starting at week 5 ($t = 5$), we shall use the observed cumulative revenues, $C_{t-1}$ to obtain the rolloing-horizon estimates of the parameters.  

In the following section, OLS regressions are performed (for $t = 5, 6, ..., 12$) and the eight sets of estimated parameters are tabulated below:  

```{r Regression, results = "asis"}
finalTable = data.frame()

# Start forecasting at t = 5
tValues <- doctorData$Week[5 : nrow(doctorData)]
for (tValue in tValues) {
    modelDoctor <- lm(St ~ I(Ctlag) + I(Ctlag^2), data = doctorData[1 : (tValue - 1), ])
    a <- modelDoctor$coefficients[1]
    b <- modelDoctor$coefficients[2]
    c <- modelDoctor$coefficients[3]
    m <- c((-b + sqrt(b^2 - 4 * a * c)) / (2 * c), (-b - sqrt(b^2 - 4 * a * c)) / (2 * c))
    m <- m[!is.nan(m) & m >= 0] # Only get the positive root
    p <- a / m
    q <- -c * m
    Ft <- predict(modelDoctor, newdata = data.frame(Ctlag = doctorData$Ctlag[tValue]))
    finalTable <- rbind(finalTable, data.frame(week = tValue, p = p, q = q, m = m, 
                                               Ft = Ft, St = doctorData$St[tValue], 
                                               row.names = NULL))
}

panderOptions('round', 3)
pander(finalTable, caption = "Rolling Horizon Estimates of p, q, m, and Ft")

```

From the above estimates, we can see that the estimated $F_t$ is quite different from the actual $S_t$. The rolloing-horizon approach may not be suitable in this case.  

